---
title: "LabExercise1"
author: "Karen Castigador"
date: "2024-02-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


``` {r}
library(polite)
library(rvest)
library(dplyr)


url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250"

session <- bow(url, user_agent = "educational purposes")
session

mpm_url <- read_html(url)
mpm_url
```
```{r}
#scraping the titles and their ranks
movie_title <- mpm_url %>%
    html_nodes("h3.ipc-title__text") %>%
    html_text()

#subset for the top 250 tv shows. Taking only 200 titles.
sub_movie <- as.data.frame(movie_title[51:250])
sub_movie

colnames(sub_movie) <- "ranks"
split_title <- strsplit(as.character(sub_movie$ranks), ".", fixed = TRUE )
split_title <- data.frame(do.call(rbind, split_title))

#remove duplicate columns
split_title <- split_title[-c(3:5)]

#rename columns
colnames(split_title) <- c("ranks","title")
split_title

#make into a data frame
rank_title <- as.data.frame(split_title)
rank_title

{r}
library(stringr)
#scraping the  rating
rating <- scrape(session) %>%
  html_nodes("span.ipc-rating-star--imdb")  %>%
html_attr("aria-label")
rating

#subset the scraped data
sub_rate <- as.data.frame(rating[51:250])
head(sub_rate)
tail(sub_rate)

#renaming the column
colnames(sub_rate) <- "rate"
split_rate <- strsplit(as.character(sub_rate$rate),".",fixed = TRUE)
split_rate <- data.frame(do.call(rbind,split_rate))

#extract only the ratings
ratings <- str_extract(sub_rate$rate, "\\d+\\.\\d+")
ratings
#make this into a data frame
rates <- as.data.frame(ratings)

{r}
#scraping vote counts
voteCount <- scrape(session) %>%
  html_nodes("span.ipc-rating-star--voteCount") %>%
  html_text

#subset the scraped data of vote counts
sub_vote <- as.data.frame(voteCount[51:250])
sub_vote


{r}
# Combine in one data frame
data1 <- data.frame(rank_title,
                    rates,
                    vote_Count = sub_vote
      

)
data1

{r}
write.csv(data1, "200TVShows.csv")

read.csv("200TVShows.csv")

{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata1 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata1)
}
tvshow1 <- c("https://www.imdb.com/title/tt0108778/reviews?ref_=tt_urv")
reviews1 <- scrape_reviews(tvshow1[1])
reviews1

{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata2 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata2)
}
tvshow2 <- c("https://www.imdb.com/title/tt0388629/reviews?ref_=tt_urv")
reviews2 <- scrape_reviews(tvshow2[1])
reviews2

{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata3 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata3)
}
tvshow3 <- c("https://www.imdb.com/title/tt0112130/reviews?ref_=tt_urv")
reviews3 <- scrape_reviews(tvshow3[1])
reviews3
{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata4 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata4)
}
tvshow4 <- c("https://www.imdb.com/title/tt5182866/reviews?ref_=tt_urv")
reviews4 <- scrape_reviews(tvshow4[1])
reviews4
```{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata5 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata5)
}
tvshow5 <- c("https://www.imdb.com/title/tt2442560/reviews?ref_=tt_urv")
reviews5 <- scrape_reviews(tvshow5[1])
reviews5

{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata6 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata6)
}
tvshow6 <- c("https://www.imdb.com/title/tt0096697/reviews?ref_=tt_urv")
reviews6 <- scrape_reviews(tvshow6[1])
reviews6

{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata7 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata7)
}
tvshow7 <- c("https://www.imdb.com/title/tt4508902/reviews?ref_=tt_urv")
reviews7 <- scrape_reviews(tvshow7[1])
reviews7


{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata8 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata8)
}
tvshow8 <- c("https://www.imdb.com/title/tt4574334/reviews?ref_=tt_urv")
reviews8 <- scrape_reviews(tvshow8[1])
reviews8

{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata9 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata9)
}
tvshow9 <- c("https://www.imdb.com/title/tt0086661/reviews?ref_=tt_urv")
reviews9 <- scrape_reviews(tvshow9[1])
reviews9
{r}
scrape_reviews <- function(url) {
page <- read_html(url)
  
title_reviews <- page %>%
    html_nodes(".title") %>%
    html_text()

#split the output to get on;y the rates without the \n.
review_split <- unlist(strsplit(title_reviews, "\n"))
review_split
 
rating_reviews <- page %>%
    html_nodes(".rating-other-user-rating") %>%
    html_text()
  
#split the output to get on;y the rates without the \n.
rate_split <- unlist(strsplit(rating_reviews, "\\s+"))
rate_split
 
dates_reviews <- page %>%
    html_nodes(".review-date") %>%
    html_text()
 
users_reviews <- page %>%
    html_nodes(".display-name-link") %>%
    html_text()
 
text_review <- page %>%
    html_nodes("div.text.show-more__control")%>%
    html_text()
 
 
  max_length <- max(length(review_split), length(rate_split), length(dates_reviews), length(users_reviews), length(text_review))
 
 
  change <- function(x, target_length) {
    if (length(x) < target_length) {
      c(x, rep(NA, target_length - length(x)))
    } else {
      x
    }
  }
 
 
  title_reviews <- change(review_split, max_length)
  rating_reviews <-change(rate_split, max_length)
  dates_reviews <- change(dates_reviews, max_length)
  users_reviews <- change(users_reviews, max_length)
  text_review <- change(text_review, max_length)
 
# Create a data frame
reviewsdata10 <- data.frame(
    Reviewers = users_reviews,
    Reviews = title_reviews,
    Ratings = rating_reviews,
    Date = dates_reviews,
    TextReviews = text_review
  )
 
  return(reviewsdata10)
}
tvshow10 <- c("https://www.imdb.com/title/tt4786824/reviews?ref_=tt_urv")
reviews10 <- scrape_reviews(tvshow10[1])
reviews10
{r}
#combined those output into one data frame using rbind
final_reviews <- rbind(reviews1,
                       reviews2,
                       reviews3,
                       reviews4,
                       reviews5,
                       reviews6,
                       reviews7,
                       reviews8,
                       reviews9,
                       reviews10
)
final_reviews
{r}
write.csv(final_reviews, "TVShowsReview.csv")

read.csv("TVShowsReview.csv")
```
